
\begin{publications}{99}

\item \textbf{Fan Yang}, Zeng-Guang Hou, Shao-Hua Mi, Gui-Bin Bian and Xiao-Liang Xie, ``Lumen Segmentation and Visualization of Abdominal Aorta Using Geodesic Active Contours for Intravascular Surgical Simulation", submitted to \textit{Robotics and Biomimetics (ROBIO), 2014 IEEE International Conference on}.%

\item \textbf{Fan Yang}, Zeng-Guang Hou, Shao-Hua Mi, Gui-Bin Bian and Xiao-Liang Xie, ``Mesh Optimization of Vessel Surface Model for Computer-Aided Simulation of Percutaneous Coronary Intervention", in \textit{Engineering in Medicine and Biology Society (EMBC), 2014 Annual International Conference of the IEEE}, August 2014, pp. 6722-6727, Chicago, USA (\textbf{oral presentation}).%

\item \textbf{YANG Fan}, HOU Zeng-Guang, MI Shao-Hua, BIAN Gui-Bin and XIE Xiao-Liang, ``Segmentation and Visualization of the Heart Region for 3-D Simulation of Coronary Intervention Procedures", in \textit{Control Conference (CCC), 2014 33rd Chinese}, July 2014, pp. 8408-8413, Nanjing, China.%

\item \textbf{Fan Yang}, Zeng-Guang Hou, Shao-Hua Mi, Gui-Bin Bian and Xiao-Liang Xie, ``Centerlines Extraction for Lumen Model of Human Vasculature for Computer-Aided Simulation of Intravascular Procedures", in \textit{Intelligent Control and Automation (WCICA), 2014 11th World Congress on}, June 2014, pp. 970-975, Shenyang, China (\textbf{oral presentation}).%

\item \textbf{Fan Yang}, Zengguang Hou, Shaohua Mi, Guibin Bian and Xiaoliang Xie, ``Tree Structures Segmentation of Coronary Arteries Using CURVES Method for Interventional Surgical Simulation", in \textit{Control and Decision Conference (2014 CCDC), The 26th Chinese}, May 2014, pp. 4600-4605, Changsha, China.%

\item \textbf{Fan Yang}, Zeng-Guang Hou, Shao-Hua Mi, Gui-Bin Bian and Xiao-Liang Xie, ``3D Modeling of Coronary Arteries Based on Tubular-Enhanced CURVES Segmented Regions for Robotic Surgical Simulation", in \textit{Robotics and Biomimetics (ROBIO), 2013 IEEE International Conference on}, December 2013, pp. 2013-2018, Shenzhen, China (\textbf{oral presentation}).%

\item Shao-Hua Mi, Zeng-Guang Hou, \textbf{Fan Yang}, Xiao-Liang Xie and Gui-Bin Bian, ``A 3D Virtual Reality Simulator for Training of Minimally Invasive", in \textit{Engineering in Medicine and Biology Society (EMBC), 2014 Annual International Conference of the IEEE}, August 2014, pp. 349-352, Chicago, USA.%

\item Shao-Hua Mi, Zeng-Guang Hou, \textbf{Fan Yang}, Xiao-Liang Xie and Gui-Bin Bian, ``A 3D Interactive Virtual Reality Software Toolkit for Minimally Invasive Vascular Surgery", in \textit{Mechatronics and Automation (ICMA), 2014 IEEE International Conference on}, August 2014, pp. 588-593, Tianjin, China.%

\item Shao-Hua Mi, Zeng-Guang Hou, \textbf{Fan Yang}, Xiao-Liang Xie and Gui-Bin Bian, ``3D Interactive Virtual Environments for Minimally Invasive Vascular Surgery", in \textit{Information and Automation (ICIA), 2014 IEEE International Conference on}, July 2014, pp. 846-851, Hailar, China.%

\item Shao-Hua Mi, Zeng-Guang Hou, \textbf{Fan Yang}, Xiao-Liang Xie and Gui-Bin Bian, ``A Collision Response Algorithm for 3D Virtual Reality Minimally Invasive Surgery Simulator", in \textit{Control and Decision Conference (2014 CCDC), The 26th Chinese}, May 2014, pp. 4594-4599, Changsha, China.%

\item Shao-Hua Mi, Zeng-Guang Hou, \textbf{Fan Yang}, Xiao-Liang Xie and Gui-Bin Bian, ``A Multi-body Mass-spring Model for Virtual Reality Training Simulators Based on a Robotic Guide Wire Operating System", in \textit{Robotics and Biomimetics (ROBIO), 2013 IEEE International Conference on}, December 2013, pp. 2031-2036, Shenzhen, China.%

\end{publications}
