%# -*- coding:utf-8 -*- 
%=========================================================================%
%   LaTeX File for phd thesis of Institute of Automation, CAS
%-------------------------------------------------------------------------%
%   Revised by J. G. Lou (jglou@nlpr.ia.ac.cn)
%-------------------------------------------------------------------------%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{攻读博士期间发表的论文\markboth{攻读博士学位期间发表的论文}{攻读博士学位期间发表的论文}}
\addcontentsline{toc}{chapter}{攻读博士学位期间发表的论文}
\begin{enumerate}
   \item[1.] \textbf{Jianguang Lou}, Tieniu Tan and Weiming Hu, "Visual vehicle tracking algorithm", ELECTRONICS LETTERS, Vol. 38, No. 18, 29th August 2002.
   \item[2.] \textbf{楼建光}，柳崎峰，胡卫明，谭铁牛, "交通视觉监控中的摄像机参数求解", 计算机学报, 第25卷, 第11册, 2002年11月.
   \item[3.] \textbf{Jianguang Lou}, Qifeng Liu, Tieniu Tan and Weiming Hu, "Semantic interpretation of object activities in a surveillance system", IEEE International Conference on Pattern Recognition, Canada, 2002 (\textbf{oral presentation}).
   \item[4.] \textbf{Jianguang Lou}, Hao Yang, Weiming Hu, Tieniu Tan, "Visual Vehicle Tracking Using An Improved EKF", the 5th Asia Conference on Computer Vision, Australia, 2002 (\textbf{oral presentation}).
   \item[5.] \textbf{Jianguang Lou}, Hao Yang, Weiming Hu, Tieniu Tan, "An Illumination Invariant Change Detection Algorithm", the 5th Asia Conference on Computer Vision, Australia, 2002 (\textbf{oral presentation}).
   \item[6.] Hao Yang, \textbf{Jianguang Lou}, Hongzan Sun, Weiming Hu and Tieniu Tan, "Efficient and robust vehicle localization", Proceeding of IEEE International Conference on Image Processing, Vol.2, pp. 355-358, Greece, 2001.
   \item[7.] Qifeng Liu, \textbf{Jianguang Lou}, Weiming Hu, Tieniu Tan, "Comparison of model-based pose evaluation algorithm in traffic scenes", the 2nd International Conference on Image and Graphics, Hefei, 2002.
   \item[8.] 柳崎峰，\textbf{楼建光}，"智能视觉监控技术"，科学新闻，第23期，pp. 35-36, 2002年12月.
\end{enumerate}

